Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-24 analysis/paper/paper.Rmd
Ran into issue of rows with NA values for dorsal cortex perc being passed into the intial PCA calc. Uploading what I have now before proceeding further.
Changed "methodology" to just "method"

  Finally, the shape landmark values were analysed by Principal Components Analysis, a form of exploratory data analysis. Our methodology for carrying out the PCA on the shape landmarks was inspired by Theska et al. (2020), which also performed 2D landmark data analysis using PCA. Principal Component Analysis takes the initial set of data and transforms the initial set of variables into a smaller set of variables whist still preserving most of the variation seen in the initial data set. PCA biplots, which plot out the first two primary components, were created to visualize differences based upon secondary categorical variables, namely flake reduction categories, excavation unit, and mass cluster. The first two primary components formulated the individual points on biplot, while the secondary variables (flake reduction categories, excavation unit, and mass clusters) were represented by colored outlines on the biplots

@@

# Note, trying to fix NA by removing all rows which lack dorsal cortex values. Issue with the intial set of data with NA values being passed through PCA. In the process of fixing

>>>>

  Finally, the shape landmark values were analysed by Principal Components Analysis, a form of exploratory data analysis. Our method for carrying out the PCA on the shape landmarks was inspired by Theska et al. (2020), which also performed 2D landmark data analysis using PCA. Principal Component Analysis takes the initial set of data and transforms the initial set of variables into a smaller set of variables whist still preserving most of the variation seen in the initial data set. PCA biplots, which plot out the first two primary components, were created to visualize differences based upon secondary categorical variables, namely flake reduction categories, excavation unit, and mass cluster. The first two primary components formulated the individual points on biplot, while the secondary variables (flake reduction categories, excavation unit, and mass clusters) were represented by colored outlines on the biplots

@@

# Note, trying to fix NA by removing all rows which lack dorsal cortex values. Issue with the initial set of data with NA values being passed through PCA. In the process of fixing
